
%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
    \newcommand{\resumeSubHeadingListEnd}{\vspace{-10pt}\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
    \newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Siksha 'O' Anusandhan University (ITER)}{Nov 2021 -- June 2025}
{Bachelor of Technology in Computer Science Engineering}{ CGPA: 9.8 }
\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
{Software Development Intern}{Sep. 2022 -- Present}
{\href{https://avetilearning.com/}{Aveti Learning Pvt. Ltd.}}{Bhubaneswar, India}
\resumeItemListStart
\resumeItem{ Developed a cross-platform AI tutor bot mobile and web application using Flutter ensuring responsiveness; utilizing OpenAI GPT-4 model through Langchain as a backend service to enhance chatbot functionality. }
% \resumeItem{ Utilized GenAI models like GPT-4 through Langchain as a backend service to enhance chatbot functionality.}
\resumeItem{ Implemented Question-Answering system using GPT-4 model, OpenAI embeddings and vector database.}
\resumeItem{ Orchestrated asynchronous RESTful APIs hosted on AWS EC2 with FastAPI and employed NGINX for scalable web server.}
% \resumeItem{ Deployed and managed Python Flask server on Linux environment in VM}
\resumeItem{Engineered micro-services architecure for translating and converting PowerPoint slides to videos within 2-month timeframe, leveraging Docker on server-less AWS Lambda functions with SQS reducing operating cost by 90\%; Integrated DynamoDB and CloudWatch for request status and error detection. }
% \resumeItem{Reduced memory consumption and cpu usage by 70\%, by analyzing system resource utilization}
\resumeItem{Optimized the deployment processes through CI/CD pipeline and achieved a 50\% time reduction via automation with Github Actions.}
\resumeItemListEnd
\resumeSubHeadingListEnd
\resumeSubHeadingListStart
\resumeSubheading
{App Development Lead}{Sep. 2023 -- Present}
{Google Developer Student Club, ITER} {Bhubaneswar, India}
\resumeItemListStart
\resumeItem { Organised sessions on Flutter basics to more than 200 students and promoted best development practices}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{\href{https://github.com/AM-ash-OR-AM-I/Passlock}{\underline{Passlock}} \& \href{https://github.com/AM-ash-OR-AM-I/PasslockDesktop}{\underline{PasslockDesktop}}} $|$ \emph{Python, Firebase, Kivy, PyInstaller, Github Actions}}{Jan. 2022 -- June 2022}
\resumeItemListStart
\resumeItem{Created a cross-platform password manager for mobile and desktop (Android, Linux, Windows). }
\resumeItem{Leveraged Firebase real-time database for efficient CRUD operations.}
\resumeItem{Implemented AES-256 encryption to ensure robust password security and decryption.}
\resumeItem{Designed real-time password synchronization system across devices with 0ms latency.}
\resumeItem{Optimized app load time by 30\% implementing lazy loading technique.}
\resumeItemListEnd

% \resumeProjectHeading
%     {\textbf{\href{https://github.com/AM-ash-OR-AM-I/AD-Programs}{\underline{Algorithm Analysis}}} $|$ \emph{ Data Structures and Algorithms (DSA) , Python, Java}}{March 2023 -- July 2023}
%     \resumeItemListStart
%       \resumeItem{ Utilized randomized quick sort to reduce time taken to sort array of 1k elements, by 40 times from 0.08s to 0.002s}
%       \resumeItem{ Analyzed and benchmarked various algorithmic techniques for practical comparison}
%       \resumeItem{Practical comparision of Karatsuba's Fast multiplication}
% \resumeItemListEnd

\resumeProjectHeading{\textbf{\href{https://github.com/AM-ash-OR-AM-I/PlantDoctor}{\underline{Plant Doctor}}} $|$ \emph{Flutter, Python, Flask, AWS, PyTorch}}{Feb 2023}
\resumeItemListStart
\resumeItem{Collaborated with a team of four in a 36-hour hackathon to create a plant health monitoring solution.}
\resumeItem{Designed and deployed ResNet ML model to achieve 90\% accuracy rate in detecting plant diseases.}
\resumeItem{Implemented offline (Raspberry Pi) and cloud-server data collection for 100\% coverage.}
\resumeItem{Integrated online marketplace for fertilizers and pesticides into the solution.}
\resumeItemListEnd

% \resumeProjectHeading
%   {\textbf{\href{https://github.com/AM-ash-OR-AM-I/Find_MyStuff}{\underline{Find MyStuff}}} $|$ \emph{ Python, Kivy, Github Actions, Git}}{Sep 2021 -- Jan 2022}
%   \resumeItemListStart
%     \resumeItem{Employed Google Speech-To-Text for voice detection}
%     \resumeItem{Successfully reduced app load time by 50\% by dynamically analyzing previous load time history.}
%     \resumeItem{Automated app build process with Github Actions}
%   \resumeItemListEnd

\resumeProjectHeading
{\textbf{\href{https://github.com/AM-ash-OR-AM-I/jaldristi}{\underline{JalDristi (Smart India Hackathon)}}} $|$ \emph{ Flutter, Python, FastAPI, MySQL }}{Sep. 2023 }
\resumeItemListStart
\resumeItem{Spearheaded a team of 6 during a 24-hour hackathon, developing a crowdsourced water-monitoring system.}
\resumeItem{Utilized Flutter and employed the Provider package for state management to craft a Neumorphic and Stateful UI.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%
%----------- Skills -----------
\vspace{-10px}
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
        \textbf{Languages}{: Python, Java, C, Dart, HTML, CSS, Assembly} \\
        % \textbf{Frameworks}{: Flutter, Flask, FastAPI, Kivy, KivyMD, TesseractOCR, PyInstaller, NumPy} \\
        \textbf{Frameworks}{: Flutter, FastAPI, Flask, Kivy, Langchain, PyInstaller, NumPy} \\
        \textbf{Tools and OS}{: Linux, UNIX shell, Bash, Git, SSH, Docker, Github Actions, Nmap, Wireshark} \\
        % \textbf{Tools and OS}{: Linux, UNIX shell, Bash, Git, SSH, Docker, Cisco Packet Tracer, Nmap, Wireshark} \\
        \textbf{Cloud Platform}{: Google Cloud Platform, Amazon Web Services} \\
        \textbf{Databases: }{Oracle DB, PostgreSQL, MySQL} \\
        }}

\end{itemize}


%
% %----------- Achievements -----------
\section{Achievements}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
        Rated 1593 (1762 Max) in \href{https://www.codechef.com/users/ashu2909}
        {\underline{Codechef}} \\
        {Rated 1596 in \href{https://leetcode.com/ashu_coderc/}{\underline{Leetcode}}} \\
        Rated 1232 (Max) Pupil in \href{https://codeforces.com/profile/ashucoder}
        {\underline{Codeforces}} \\
        Secured \textbf{4th} rank in Capture The Flag contest conducted by NIT Rourlkela \\
        }}

\end{itemize}
